ms_figures

### 2023-04-28 ms_figures.Rmd

fig3c <- fig3c_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

>>>>

fig3c <- ggplot() +
  geom_ribbon(data = fig3c_data %>%
                filter(supply_source == "domestic"),
              aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  geom_ribbon(data = fig3c_data %>%
                filter(supply_source == "foreign"),
              aes(ymin = supply_min_percent, ymax = supply_max_percent, x = year), fill = "grey70") +
  geom_line(data = fig3c_data, aes(x = year, y = supply_percent, color = supply_source)) +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
